Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-22 SupportingInformation.Rmd
adding discussion(primarily) and fixing figures

  if(ploton==T){
    if(rawplot==T){
      op<-par(mar=c(5.1, 5.1, 1.5, 2.1))
      plot(tab_dbp$avg.H,tab_dbp$avg.Biomass,xlab="avg.H",ylab="avg.Biomass",col="red",pch=1,cex.lab=2.5,cex.axis=1.5)
      mtext(paste0("Year=",year),cex=2)
      par(op)
    }else{
      op<-par(mar=c(5.1, 5.1, 1.5, 2.1))
      plot(cop_tab_dbp$avg.H,cop_tab_dbp$avg.Biomass,xlab="u",ylab="v",col="red",pch=1,cex.lab=2.5,cex.axis=1.5,
         xlim=c(0,1),ylim=c(0,1),asp=1)
      rect(0,0,1,1)
      lines(c(0,1),c(0,1),type='l')
      mtext(paste0("Year=",year),cex=2)
      par(op)
    }
  }

@@

d1<-data_aphid_count$`Green spruce aphid`[[4]]
d2<-data_aphid_count$`Green spruce aphid`[[11]]
pdf("./Results/Aphid_count_raw_loc_4_11.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(d1$Dat,d2$Dat,type="p",col="red",xlab="Green-spruce aphid count (loc. 4)",ylab="Green-spruce aphid count (loc. 11)",cex.lab=2.5,cex.axis=1.5)
par(op)
dev.off()

source("./vivj_matrix.R")
m<-vivj_matrix(d_allsp = data_aphid_count,sp=10,i=4,j=11)
pdf("./Results/Aphid_count_cop_loc_4_11.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(m[,1],m[,2],type="p",col="red",xlab="u",ylab="v",
     cex.lab=2.5,cex.axis=1.5,
     xlim=c(0,1),ylim=c(0,1),asp=1)
rect(0,0,1,1)
lines(c(0,1),c(0,1),type='l')
par(op)
dev.off()

# code to plot raw data and copula plot for aphid ff @location pair (2,5)
# bestfit cop : J
d1<-data_aphid_ff$`Leaf-curling plum aphid`[[2]]
d2<-data_aphid_ff$`Leaf-curling plum aphid`[[5]]
pdf("./Results/Aphid_ff_raw_loc_2_5.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(d1$Dat,d2$Dat,type="p",col="red",xlab="Leaf-plum curling's first-flight (loc. 2)",ylab="Leaf-plum curling's first-flight (loc. 5)",cex.lab=2.5,cex.axis=1.5)
par(op)
dev.off()

m<-vivj_matrix(d_allsp = data_aphid_ff,sp=11,i=2,j=5)
pdf("./Results/Aphid_ff_cop_loc_2_5.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(m[,1],m[,2],type="p",col="red",xlab="u",ylab="v",
     cex.lab=2.5,cex.axis=1.5,
     xlim=c(0,1),ylim=c(0,1),asp=1)
rect(0,0,1,1)
lines(c(0,1),c(0,1),type='l')
par(op)
dev.off()
```

@@

splist<-c(1:20)
skw_aphid_count_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_count_spearman)<-c("realskw","p_left","p_right")
rownames(skw_aphid_count_spearman)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_count/aphid_count_allsp_skewness_spearman.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
cat("Now for spearman preserving surrogs : aphid count","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_count,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_count),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_count_spearman$realskw[i]<-ans$realskw
  skw_aphid_count_spearman$p_left[i]<-p_left
  skw_aphid_count_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_count_spearman,"./Results/skewness_results/skewness_aphid_count/skw_aphid_count_spearman.RDS")

skw_aphid_count_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_count_kendall)<-c("realskw","p_left","p_right")
rownames(skw_aphid_count_kendall)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_count/aphid_count_allsp_skewness_kendall.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
cat("Now for kendall preserving surrogs : aphid count","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_count,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_count),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_count_kendall$realskw[i]<-ans$realskw
  skw_aphid_count_kendall$p_left[i]<-p_left
  skw_aphid_count_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_count_kendall,"./Results/skewness_results/skewness_aphid_count/skw_aphid_count_kendall.RDS")
```

@@

splist<-c(1:20)
skw_aphid_ff_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_ff_spearman)<-c("realskw","p_left","p_right")
rownames(skw_aphid_ff_spearman)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_ff/aphid_ff_allsp_skewness_spearman.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
cat("Now for spearman preserving surrogs : aphid ff","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_ff,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_ff),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_ff_spearman$realskw[i]<-ans$realskw
  skw_aphid_ff_spearman$p_left[i]<-p_left
  skw_aphid_ff_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_ff_spearman,"./Results/skewness_results/skewness_aphid_ff/skw_aphid_ff_spearman.RDS")

skw_aphid_ff_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_ff_kendall)<-c("realskw","p_left","p_right")
rownames(skw_aphid_ff_kendall)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_ff/aphid_ff_allsp_skewness_kendall.pdf",height=20,width=20)
op<-par(mfrow=c(4,5),mar=c(4.2,5,1,1),mgp=c(3,1,0))
cat("Now for kendall preserving surrogs : aphid ff","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_ff,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_ff),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_ff_kendall$realskw[i]<-ans$realskw
  skw_aphid_ff_kendall$p_left[i]<-p_left
  skw_aphid_ff_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_ff_kendall,"./Results/skewness_results/skewness_aphid_ff/skw_aphid_ff_kendall.RDS")
```

@@

splist<-c(1:22)
skw_plankton_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_plankton_spearman)<-c("realskw","p_left","p_right")
rownames(skw_plankton_spearman)<-paste("sp",splist,sep="")
skw_plankton_kendall<-skw_plankton_spearman
pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_spearman.pdf",height=24,width=24)
op<-par(mfrow=c(4,6),mar=c(4.2,5,1,1),mgp=c(3,1,0))
#cat("Now for spearman preserving surrogs : pns","\n")
for(i in splist){
  #cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_plankton_spearman$realskw[i]<-ans$realskw
  skw_plankton_spearman$p_left[i]<-p_left
  skw_plankton_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_plankton_spearman,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_spearman.RDS")

pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_kendall.pdf",height=24,width=24)
op<-par(mfrow=c(4,6),mar=c(4.2,5,1,1),mgp=c(3,1,0))
#cat("Now for kendall preserving surrogs : pns","\n")
for(i in splist){
  #cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_plankton_kendall$realskw[i]<-ans$realskw
  skw_plankton_kendall$p_left[i]<-p_left
  skw_plankton_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_plankton_kendall,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_kendall.RDS")
```

@@

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_kendall.pdf",height=6,width=8)
op<-par(mar=c(3.5,3.5,1.8,0.1), mgp=c(2, 1, 0))
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_left<-sum(answer1k$surrogskw < answer1k$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf",height=6,width=8)
op<-par(mar=c(3.5,3.5,1.8,0.1), mgp=c(2, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman")

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_kendall.pdf",height=6,width=8)
op<-par(mar=c(3.5,3.5,1.8,0.1), mgp=c(2, 1, 0))
answer2k<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_right<-sum(answer2k$surrogskw > answer2k$realskw)/numsurrog
mtext(paste0("p = ",p_right),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf",height=6,width=8)
op<-par(mar=c(3.5,3.5,1.8,0.1), mgp=c(2, 1, 0))
answer2s<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman") 
p_right<-sum(answer2s$surrogskw > answer2s$realskw)/numsurrog
mtext(paste0("p = ",p_right),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_kendall.pdf",height=6,width=8)
op<-par(mar=c(3.5,3.5,1.8,0.1), mgp=c(2, 1, 0))
answer3k<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_left<-sum(answer3k$surrogskw < answer3k$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf",height=6,width=8)
op<-par(mar=c(3.5,3.5,1.8,0.1), mgp=c(2, 1, 0))
answer3s<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman") 
p_left<-sum(answer3s$surrogskw < answer3s$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane_kendall.pdf",height=6,width=8)
op<-par(mar=c(3.5,3.5,1.8,0.1), mgp=c(2, 1, 0))
answer1k<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="kendall") 
p_left<-sum(answer1k$surrogskw < answer1k$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()

pdf("./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf",height=6,width=8)
op<-par(mar=c(3.5,3.5,1.8,0.1), mgp=c(2, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="spearman") 
p_left<-sum(answer1s$surrogskw < answer1s$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()
```

>>>>

  if(ploton==T){
    if(rawplot==T){
      op<-par(mar=c(5.1, 5.1, 1.5, 2.1))
      plot(tab_dbp$avg.H,tab_dbp$avg.Biomass,xlab="avg.H",ylab="avg.Biomass",col="red",pch=1,cex.lab=2,cex.axis=1.5)
      mtext(paste0("Year=",year),cex=2)
      par(op)
    }else{
      op<-par(mar=c(5.1, 5.1, 1.5, 2.1))
      plot(cop_tab_dbp$avg.H,cop_tab_dbp$avg.Biomass,xlab="u",ylab="v",col="red",pch=1,cex.lab=2,cex.axis=1.5,
         xlim=c(0,1),ylim=c(0,1),asp=1)
      rect(0,0,1,1)
      lines(c(0,1),c(0,1),type='l')
      mtext(paste0("Year=",year),cex=2)
      par(op)
    }
  }

@@

d1<-data_aphid_count$`Green spruce aphid`[[4]]
d2<-data_aphid_count$`Green spruce aphid`[[11]]
pdf("./Results/Aphid_count_raw_loc_4_11.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(d1$Dat,d2$Dat,type="p",col="red",xlab="Green-spruce aphid count (loc. 4)",ylab="Green-spruce aphid count (loc. 11)",cex.lab=2.5,cex.axis=2)
par(op)
dev.off()

source("./vivj_matrix.R")
m<-vivj_matrix(d_allsp = data_aphid_count,sp=10,i=4,j=11)
pdf("./Results/Aphid_count_cop_loc_4_11.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(m[,1],m[,2],type="p",col="red",xlab="u",ylab="v",
     cex.lab=3,cex.axis=2,
     xlim=c(0,1),ylim=c(0,1),asp=1)
rect(0,0,1,1)
lines(c(0,1),c(0,1),type='l')
par(op)
dev.off()

# code to plot raw data and copula plot for aphid ff @location pair (2,5)
# bestfit cop : J
d1<-data_aphid_ff$`Leaf-curling plum aphid`[[2]]
d2<-data_aphid_ff$`Leaf-curling plum aphid`[[5]]
pdf("./Results/Aphid_ff_raw_loc_2_5.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(d1$Dat,d2$Dat,type="p",col="red",xlab="Leaf-plum curling's first-flight (loc. 2)",ylab="Leaf-plum curling's first-flight (loc. 5)",cex.lab=2.5,cex.axis=2)
par(op)
dev.off()

m<-vivj_matrix(d_allsp = data_aphid_ff,sp=11,i=2,j=5)
pdf("./Results/Aphid_ff_cop_loc_2_5.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(m[,1],m[,2],type="p",col="red",xlab="u",ylab="v",
     cex.lab=3,cex.axis=2,
     xlim=c(0,1),ylim=c(0,1),asp=1)
rect(0,0,1,1)
lines(c(0,1),c(0,1),type='l')
par(op)
dev.off()
```

@@

splist<-c(1:20)
skw_aphid_count_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_count_spearman)<-c("realskw","p_left","p_right")
rownames(skw_aphid_count_spearman)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_count/aphid_count_allsp_skewness_spearman.pdf",height=25,width=25)
op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
cat("Now for spearman preserving surrogs : aphid count","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_count,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_count),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_count_spearman$realskw[i]<-ans$realskw
  skw_aphid_count_spearman$p_left[i]<-p_left
  skw_aphid_count_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_count_spearman,"./Results/skewness_results/skewness_aphid_count/skw_aphid_count_spearman.RDS")

skw_aphid_count_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_count_kendall)<-c("realskw","p_left","p_right")
rownames(skw_aphid_count_kendall)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_count/aphid_count_allsp_skewness_kendall.pdf",height=25,width=25)
op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
cat("Now for kendall preserving surrogs : aphid count","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_count,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_count),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_count_kendall$realskw[i]<-ans$realskw
  skw_aphid_count_kendall$p_left[i]<-p_left
  skw_aphid_count_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_count_kendall,"./Results/skewness_results/skewness_aphid_count/skw_aphid_count_kendall.RDS")
```

@@

splist<-c(1:20)
skw_aphid_ff_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_ff_spearman)<-c("realskw","p_left","p_right")
rownames(skw_aphid_ff_spearman)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_ff/aphid_ff_allsp_skewness_spearman.pdf",height=25,width=25)
op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
cat("Now for spearman preserving surrogs : aphid ff","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_ff,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_ff),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_ff_spearman$realskw[i]<-ans$realskw
  skw_aphid_ff_spearman$p_left[i]<-p_left
  skw_aphid_ff_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_ff_spearman,"./Results/skewness_results/skewness_aphid_ff/skw_aphid_ff_spearman.RDS")

skw_aphid_ff_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_ff_kendall)<-c("realskw","p_left","p_right")
rownames(skw_aphid_ff_kendall)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_ff/aphid_ff_allsp_skewness_kendall.pdf",height=25,width=25)
op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
cat("Now for kendall preserving surrogs : aphid ff","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_ff,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_ff),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_ff_kendall$realskw[i]<-ans$realskw
  skw_aphid_ff_kendall$p_left[i]<-p_left
  skw_aphid_ff_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_ff_kendall,"./Results/skewness_results/skewness_aphid_ff/skw_aphid_ff_kendall.RDS")
```

@@

splist<-c(1:22)
skw_plankton_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_plankton_spearman)<-c("realskw","p_left","p_right")
rownames(skw_plankton_spearman)<-paste("sp",splist,sep="")
skw_plankton_kendall<-skw_plankton_spearman
pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_spearman.pdf",height=30,width=30)
op<-par(mfrow=c(4,6),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for spearman preserving surrogs : pns","\n")
for(i in splist){
  #cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_plankton_spearman$realskw[i]<-ans$realskw
  skw_plankton_spearman$p_left[i]<-p_left
  skw_plankton_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_plankton_spearman,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_spearman.RDS")

pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_kendall.pdf",height=30,width=30)
op<-par(mfrow=c(4,6),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for kendall preserving surrogs : pns","\n")
for(i in splist){
  #cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_plankton_kendall$realskw[i]<-ans$realskw
  skw_plankton_kendall$p_left[i]<-p_left
  skw_plankton_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_plankton_kendall,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_kendall.RDS")
```

@@

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_kendall.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_left<-sum(answer1k$surrogskw < answer1k$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman")

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_kendall.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer2k<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_right<-sum(answer2k$surrogskw > answer2k$realskw)/numsurrog
mtext(paste0("p = ",p_right),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer2s<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman") 
p_right<-sum(answer2s$surrogskw > answer2s$realskw)/numsurrog
mtext(paste0("p = ",p_right),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_kendall.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer3k<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_left<-sum(answer3k$surrogskw < answer3k$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer3s<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman") 
p_left<-sum(answer3s$surrogskw < answer3s$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane_kendall.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1k<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="kendall") 
p_left<-sum(answer1k$surrogskw < answer1k$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()

pdf("./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="spearman") 
p_left<-sum(answer1s$surrogskw < answer1s$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,col="navyblue",cex = 2)
par(op)
dev.off()
```
